A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
typo fixed

\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge. The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow C\times \Sigma$ together with a connection $A$ and a section $\phi\in\Gamma(C\times \Sigma, \mathrm{ad} P)$ which satisfy
\begin{align}
(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
\d^*_A \phi &= 0.
\end{align}
Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.

>>>>

\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge. The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
\begin{align}
(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
\d^*_A \phi &= 0.
\end{align}
Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
